\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lipsum,turnthepage}
\renewcommand{\turnthepage}{\itshape Please turn over...}

\begin{document}

\pagestyle{empty}

\begin{center}
    \textbf{{\LARGE Sherry Thomas}} \\
    \href{https://github.com/SherryS997}{GitHub} | \href{https://www.kaggle.com/iveeaten3223times}{Kaggle} | \href{https://www.linkedin.com/in/sherry-thomassp/}{LinkedIn} | \href{https://sherrys997.github.io/}{Portfolio} \\
    \textit{Indian Institute of Technology Madras}
\end{center}

\section*{Introduction}
Highly motivated Data Science student at IIT Madras (BS in Data Science and Applications, expected 2025) with a passion for Large Language Models (LLMs) and Natural Language Processing (NLP). Proven ability to contribute effectively through research, teaching, and open-source projects. Eager to leverage strong technical skills and a background in philosophy to solve real-world problems.

\section*{Projects}
\textbf{Indic Parler-TTS} \\
Link: \url{https://huggingface.co/ai4bharat/indic-parler-tts/}  
\begin{itemize}[noitemsep]
    \item Developed multilingual TTS model for 21 languages (20 Indic + English).
    \item Enabled fine-grained control over speech characteristics via text prompts.
    \item Curated and cleaned 8,385-hour multilingual speech dataset.
    \item Contributed to training setup, performance monitoring, and troubleshooting.
\end{itemize}
\textbf{Blog-Lite v2 (Vue3, Python-Flask)} \\
Link: \url{https://github.com/SherryS997/Blog-Lite-v2}  
\begin{itemize}[noitemsep]
    \item Awarded 'Best Project'. Part of course-work.
    \item Platform for text/image blogs, enabling user interactions with Flask REST API, Celery, & Redis.
    \item Tech Stack: Vue3, Python, Flask, SQLite, Redis, Celery
\end{itemize}
\textbf{Machine Learning Algorithms (Quarto, Markdown, LaTeX)} \\
Link: \url{https://github.com/SherryS997/Machine-Learning-Algorithms}  
\begin{itemize}[noitemsep]
    \item Comprehensive resource on ML algorithm foundations.
    \item Adopted by IIT Madras as course notes.
    \item Tech Stack: Python, Scikit-Learn, Pandas, TensorFlow
\end{itemize}

\section*{Publications}
\textbf{IndicVoices-R: Unlocking a Massive Multilingual Multi-speaker Speech Corpus for Scaling Indian TTS} \\
NeurIPS (2024)
\begin{itemize}[noitemsep]
    \item Created large IndicVoices-R dataset for multilingual Indian text-to-speech.
    \item Benchmark evaluates zero-shot Indian TTS, model improves generalization.
\end{itemize}
\textbf{RASMALAI} \\
Interspeech (2025)
\begin{itemize}[noitemsep]
    \item Introduces RASMALAI, a large multilingual dataset for controllable text-to-speech.
    \item Develops IndicParlerTTS, a controllable multilingual text-to-speech model.
\end{itemize}
\textbf{The State Of TTS: A Case Study with Human Fooling Rates} \\
Interspeech (2025)
\begin{itemize}[noitemsep]
    \item Introduces Human Fooling Rate (HFR) to directly measure speech indistinguishability.
    \item Reveals CMOS-based parity claims are misleading via HFR evaluation of TTS systems.
\end{itemize}

\section*{Work Experience}
\textbf{Data Science Intern} \\
AI4Bhārat, IIT Madras (February 2024 - Present)
\begin{itemize}[noitemsep]
    \item Contributing to the TTS Lab by cleaning, preparing data, and training models.
    \item Building open-source text-to-speech (TTS) models for the 22 official languages of India.
\end{itemize}
\textbf{ML Research Intern} \\
IIT Madras (Sept 2023-Jan 2024)
\begin{itemize}[noitemsep]
    \item Developing content bridging theory and practice in classical ML.
    \item Creating high-quality ML notebooks exploring model internals and guiding effective EDA and model building.
\end{itemize}
\textbf{Machine Learning Techniques (CS2007) TA} \\
IIT Madras (May-Aug 2023)
\begin{itemize}[noitemsep]
    \item Prepared comprehensive course notes adopted as standard course material.
    \item Mentored students, conducted sessions on classical ML topics, and created tutorial content.
    \item Recorded companion sessions, enhancing course accessibility.
\end{itemize}

\section*{Education}
\begin{tabular}{llll}
    \textbf{Program} & \textbf{Institution} & \textbf{CGPA} & \textbf{Year} \\
    BS in Data Science and Applications & IIT Madras & 9.65 & 2025 \\
    BA in Philosophy & Christ University, Bengaluru & 9.57 & 2021 \\
\end{tabular}

\section*{Certifications}
\textbf{Deep Learning Specialization} \\
Completed 5 courses mastering CNNs, RNNs, LSTMs, Transformers, and optimization techniques in neural networks for applications like speech recognition and NLP. \\
Link: \url{https://coursera.org/share/6dfedef63e8fbd72284092cb7c5b0da9}\\
\textbf{Generative AI with Large Language Models} \\
Acquired learning in LLM lifecycle, training, fine-tuning, and deployment strategies for real-world applications, understanding business implications from industry insights. \\
Link: \url{https://coursera.org/share/abd98e71f4b17faa5c391bc2aceff982}

\section*{Positions of Responsibility}
\textbf{Senate Member} \\
Christ University, 2019-20
\begin{itemize}[noitemsep]
    \item Actively contributed as a member of the Senate, the highest governing body.
    \item Participated in crucial meetings addressing important matters.
\end{itemize}
\textbf{Student Council Member} \\
Philosophy Department, Christ University, 2020-21
\begin{itemize}[noitemsep]
    \item Helped out in Department Budgeting.
    \item Organized the Annual Fest and various departmental events throughout the academic year.
\end{itemize}

\section*{Skills}
\textbf{Languages:} Python, JavaScript, Java, SQL \\
\textbf{Web:} HTML, CSS, Vue.js \\
\textbf{Tools:} TensorFlow, PyTorch, OpenCV, Scikit-learn, Pandas, Flask, Django, Sqlalchemy \\
\textbf{NLP:} llama.cpp, Langchain, Llama LLM, Mistral LLM, Bloom LLM, Flan-t5

\end{document}
